combine all centers pheno

### 2020-12-14 scripts/40_combine_all_samp_pheno.Rmd
going slowly but moving forward....
working hard this weekend I think I can actually take a break

@@

all %>% 
  count(center, cr_d30)
```

>>>>

```{r}
I2 <- read_csv('../data/shotgun_pheno/italy_all_later.csv')

P <- read_csv('../data/shotgun_pheno/upenn_all_earlier.csv')

P2 <- read_csv('../data/shotgun_pheno/upenn_all_later.csv')

M <- read_csv('../data/shotgun_pheno/msk_all_pheno.csv')
```

@@

all %>% 
  count(center, cr_d30)

# output a final format with only the most essential columns
all %>% 
  select(fid, cr_d30, toxicity, center) %>% 
  mutate(cr_d30 = str_to_lower(cr_d30)) %>% 
  write_csv('../data/shotgun_pheno/final_simplified.csv')

all %>% 
  write_csv('../data/shotgun_pheno/final_comprehensive.csv')

all %>% 
  write_csv('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/shotgun_results/pheno_data_CR_toxicity_comprehensive.csv')
```
